ScPy: A SuperCollider Extension for Performing Numerical Computation via Embedded Python

### 2016-08-28 doc/paper.tex
radial graphs in latex are easy!

\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{minted}
\usepackage[style=numeric-comp]{biblatex}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{tikz}

@@

\begin{figure}[ht]
\caption{NIME dimension space analysis for ScPy.}
\vspace{1em}
\includegraphics[scale=0.2]{nime-plot}
\label{fig:nime}
\end{figure}

>>>>

\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{minted}
\usepackage[style=numeric-comp]{biblatex}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{tkz-kiviat}

@@

\begin{figure}[ht]
    \caption{NIME dimension space analysis for ScPy.}\label{fig:nime}
    \begin{center}
        \begin{tikzpicture}[rotate=-116,xscale=-1]
            \tkzKiviatDiagram[label distance=.5cm,
                    radial=7,
                    gap=0.75,
                    lattice=4]{Required Expertise,
                    Musical Control,
                    Degrees of Freedom (Inputs),
                    Feedback Modalities (Outputs),
                    Inter-actors,
                    Distribution in Space,
                    Role of Sound}
            \tkzKiviatLine[thick,color=blue,mark=none,
                           fill=blue!20,opacity=.5](4,4,1.5,1.5,0.5,0.5,3)
        \end{tikzpicture}
    \end{center}
\end{figure}
